How residence time constrains diversity

### 2015-06-10 analyses/ResTime_GeneralResults.Rmd

simulation <- sim.data$sim
height <- sim.data$Height
width <- sim.data$Width
flow.rate <- sim.data$FlowRate

@@

>>>>

sim <- sim.data$sim # the specific simulation run
height <- sim.data$Height
width <- sim.data$Width
flow.rate <- sim.data$FlowRate

@@

sim.sub <- subset(sim.data, sim == 60)
height <- sim.sub$Height
width <- sim.sub$Width
flow.rate <- sim.sub$FlowRate

h.tau <- log((height * width)/flow.rate)
m.tau <- log(sim.sub$cell.tau)
t.tau <- log(sim.sub$particle.tau)

N <- sim.sub$N
S <- sim.sub$S
e.var <- sim.sub$e.var
e.simp <- sim.sub$simpson.e
avg.ab <- N/S
Skew <-sim.sub$skew
Nmax <- sim.sub$N.max
SimpD <- sim.sub$SD

plot(t.tau, N, xlab="Particle Residence Time", 
     ylab="Total Abundance", 
     main = "N vs. Tau", col='cornsilk4')
lines(t.tau, N)

plot(t.tau, S, xlab="Particle Residence Time", 
     ylab="Species Richness", 
     main = "S vs. Tau", col='darkseagreen')
lines(t.tau, S)
